Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2023-04-24 docs/manuscript/manuscript.tex
Edit current evidence sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Introduction}
Reproducibility as a characteristic of a study that lends it credibility v. Reproducibility as a error correcting function of science.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Assessing the Reproducibility of Research}
The reproducibility of research can be assessed directly or indirectly. 
In a direct assessment of reproducibility, an independent team(s) of researchers repeats the analytical steps of a previous study using the same data and then evaluates the consistency of the two sets of results\footnote{Insert paragraph on the difficulty of developing in using consistency criteria}.
Direct reproducibility assessments aim to establish whether the data and analysis presented in support of a result do in fact support that result.
By contrast, indirect assessments of reproducibility aim to establish whether study data and procedures are presented with sufficient transparency and clarity that research results could be subjected to a direct assessment. 
During an indirect assessment of reproducibility, a research team gathers information about the transparency of a study and the availability of the research components (e.g., data and code) needed to recreate that study, but does not directly attempt to recreate the results. 
Indirect assessments also often take the form of surveys in which researchers are asked about their research practices, incentives, and motivations to measure the transparency and practices of a subset if researchers.

Direct and indirect reproducibility assessments present a trade off between the depth and breadth of evaluation.  
A direct assessment can provide insight into how a particular study was conducted and why a consistent result could, or could not, be obtained.  
However, such assessments are resource and time intensive, which makes them difficult to scale to a large number of studies. 
Constrained to a limited number of studies, direct assessments offer only suggestive evidence about the reproducibility of unevaluated studies and the prevalence of reproducible research practices. 
In contrast, comparatively less resource intensive indirect assessments that simply catalog reproducible research practices can be more easily scaled.
By evaluating many studies, indirect assessments provide evidence of how common reproducible research practices are and, by extension, how reproducible work in a field of study is likely to be.

Despite their growing number, the available body of direct and indirect reproducibility assessments currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically \citep{NASEM2019}.
This knowledge gap exists because neither direct nor indirect reproducibility assessments have been designed so the results of the sample of studies evaluated can be extended to the population of research as a whole. 
Reproduction attempts remain relatively rare, and those that do exist \citep[see][]{chang2015economics, moraila2014measuring} have selectively targeted publications in high-impact journals and conference papers series in a limited number of disciplines that are not representative of many forms of research.    
Indirect reproducibility assessments similarly focus on conveniently accessible archives, such as conference paper series \citep{gundersen2018state, ostermann2017}, or target specific journals and disciplinary repositories \citep{stodden2018empirical, stodden2018enabling, byrne_2017}.
These assessments have also tended to focus on evaluating the computational components of research such as data and code availability, as this information is easier to identify and assess at scale when compared to components like field procedures or qualitative analysis that may be included only in text. 
Surveys of researcher practices and attitudes on reproducibility face similar challenges. 
Rather than carefully defining researcher populations of interest, existing surveys have drawn data non-randomly from self-selecting populations that are convenient to survey (e.g., members of professional association, conference attendees), but are not necessarily representative of researchers active in a particular field. 
These surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response.

While it may not be possible to determine the extent of irreproducibility across or within disciplines from available studies, it is possible to draw lessons about potential sources of irreproducibility.
The available evidence suggests inadequate record keeping, opaque reporting, unavailable research components, and a lack of incentives are likely important factors contributing to the irreproducibility of research \citep{NASEM2019}. 
Prominent attempts to reproduce research in economics \citep{chang2015economics}, computer science \citep{moraila2014measuring}, and psychology \citep{open2015estimating} have all been able to reproduce only a small portion of studies because original authors did not share data or adequate information about their procedures. 
Systematic reviews of publications in prominent outlets \citep{byrne_2017,stodden2018empirical} suggest these issues are likely widespread. 
Reproducibility surveys paint a similar picture. 
Recent surveys suggest that the majority of scientists have either not tried, or tried and failed to reproduce another scientist's work \citep{baker20161, boulbes2018survey}. 
Moreover, a sizable portion of the researchers responding to these surveys admit to engaging in questionable research practices linked to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.
For example, in a survey of 807 ecologists and evolutionary biologists, 64 percent admitted to failing to report non-significant results and 51 percent admitted to presenting unexpected findings as if they had been hypothesized from the start of the research \citep{fraser2018questionable}.  
These findings match researcher perceptions, which link irreproducibility to causes ranging from natural variation to outright fraud \citep{ranstam2000fraud, anderson2007normative, baker20161}.

\subsection*{Assessing the Reproducibility of Geographic Research}
To date, only a small number of studies have attempted to reproduce geographic research.
The reproductions that are available within the discipline suggest that many studies cannot be fully reproduced \citep{Kedron2021ssrn, nust2018, ostermann2021}, or are simply missing the components needed to attempt a reproduction \citep{Kedron_VijayanRP, konkol2019, ostermann2021}.

For example, \citet{ostermann2021}'s attempt to reproduce the computational analyses of 75 papers published in the GIScience conference series found that most results could not be reproduced, or could only be reproduced with significant effort. 
A related effort to reproduce 31 papers published in the conference series of the Association of Geographic Information Laboratories in Europe \citep{Nust_AGILE_2020, Nust2021AGILE, Nust_AGILE_2022} identified the inaccessibility of data, code, and information about the computational environment as key barriers to recreating results. 
\citet{konkol2019}'s attempt to reproduce of 41 geocomputational studies likewise found that 39 of the papers had coding issues that hindered reproduction and that 47 percent of the figures created using the original data and code deviated from the those published in some significant way (e.g., graphs with different curves).

Moving past the question of whether the computational results of a study can be recreated using the same data and code, a handful of geographic researchers are using the reproduction process as a way of examining not only the execution of a prior study, but its conceptualization and inferences \citep{Kedron_MollaloRP, Kedron_SaffaryRP, Kedron_VijayanRP}. 
While this form of the direct approach to reproduction opens a new door to the critical evaluation of geographic research, it primarily provides evidence about a particular research study and the phenomenon that study investigates. 
Similarly, while computationally focused reproductions have produced useful guidelines \citep{hofer2019reproducible, wilson2021} and moved forward the development of the computational and institutional infrastructure \citep{Kedron_Holler_Bardin_Hilgendorf_2022, nust2019, nust2021,}\textbf{ADD SHAOWEN} needed to foster reproducibility in the field, they have not yet assessed the use of reproducible research practices across the disciplines diverse research traditions, or identified the factors that have barred geographers from adopting practices that foster reproducibility or from conducting more reproduction studies.

To date only a handful studies have tried to indirectly measure the reproducibility of geographic research.
In a survey of participants from the 2016 European Geosciences Union General Assembly, \citet{konkol2019} assessed the frequency with which researchers published their work in ways that enabled computational reproducibility. 
Those authors found that only 33 percent of respondents included links to the data used in their analyses and only 12 percent provided their analytical code. 
The authors also found that only seven percent of respondents ever attempted to reproduce the work of other researchers.
For example, \citet{ostermann2017} use a literature review of volunteered geographic information research publications to assess computational reproducibility based on availability of original data, metadata, source code, or pseudocode.
Remote Sensing survey.

\subsubsection*{Research Summary to Transition}
The evidence available from direct and indirect assessments of reproducibility suggests that studies are often not reproducible because researchers do provide the information or materials others need to recreate their work.

However, may of our indirect assessment are on shaky methodological grounds and we have not studied this in geography.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data and Methods}
Complete documentation of the procedures and materials used in this study are available through the Survey of Reproducibility in Geographic Research Repository (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF).
That repository connects to a Github repository which hosts the anonymized dataset and code used to create all results and supplemental materials and along with a complete history of their development. 
Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_Survey_PAP} - \url{https://osf.io/6zjcp}). 
We later amended that plan to reflect a change in stopping rule we used to end the survey and to include additional statistical analyses we conducted after viewing the survey response.

The survey was conducted under the approval and supervision of the Arizona State Institutional Review Board - \textit{STUDY00014232}.
All approved documentation, study protocols, and consent materials are available through the above repository.

@@

Second, we used Arizona State University's institutional subscription to the \href{https://www.scopus.com/home.uri}{Scopus Database} to extract journal information (e.g., subject area, ranking), article information (e.g., abstract, citation counts), and author information (e.g., corresponding status, email) for each publication. 
Because our intention is to capture individuals actively publishing new geographic research, we retained publications indexed by Scopus as \textit{document type = "Article"} and removed all other publication types (e.g., editorials, book reviews) from our article database. 
We also removed articles with missing authorship information.

Third, we next moved to the author level to create a condensed list of corresponding authors. 
We chose to focus on corresponding authors for two reasons. 
(1) Corresponding authorship is one indicator of the level of involvement an individual had in a given work. 
While imperfect, it was the best available indicator in the Scopus database as across journals there is no commonly adopted policy for declarations of author work (e.g., CRediT Statements).
(2) Scopus maintains email contact information for all corresponding authors, which gave us a means of contacting researchers in our sampling frame.
Scopus also maintains a unique identifier for each author (author-id) across time, which allowed us to identify authors across publications.

Fourth, we associated each corresponding author with their contact email address and deduplicated to create a single record for each corresponding author. 
To maximize our chance or response, we retained the latest available contact information for each author by sorting the initial list by author-id and publication year (descending) and keeping the latest available entry for each author-id. 
For authors who had two or more distinct emails in the latest year of publication, we deduplicated by giving a ranked preference to .edu, .gov, and then .org extensions.

Applying these criteria yielded a sampling frame of 29,828 authors. 
On average, these authors published 2.7 articles in geography journals meeting our criteria between 2017 and 2021. 
Roughly one-third (33 percent) were most recently a corresponding author for an article published in a general geography journal. 
A similar proportion (32 percent) were most recently a corresponding author for an article published in an earth sciences journal, and smaller proportions in the social sciences and cultural geography (20 percent and 16 percent, respectively).

\subsection*{Survey Instrument}
The survey instrument used in this study is available through the Survey of Reproducibility in Geographic Research Repository.
The survey consists of 23 questions that assess (i) perceptions of the reproducibility of geographic research, (ii) familiarity and use of reproducible research practices, and (iii) beliefs about barriers to reprodicibility, and (iv) experience conducting independent reproductions. 
Survey questions were developed following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility literature. 
All researchers were presented questions about their definition of reproducibility, familiarity with and use of reproducible practices, and perceptions of barriers to reproducibility. 
However, a subset of researchers that reported attempting to reproduce a study in the past two years were given an additional set of questions about their experience conducting that work.

Because this survey had not been previously fielded, we pilot tested the instrument with a subset of \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
After pilot testing we removed these individuals from our sampling frame to ensure they would not be included in our final sample.

@@

%%%%%%%%%%%
\subsubsection*{Statistical Approach}
We conduct two statistical analyses of the survey response\endnote{The full methodological details of our statistical analyses, and a complete history of our response coding a variable construction is included in the Github repository linked to OSF repository that accompanies this paper. All of the results presented in this paper can be independently reproduced using the materials in that repository.}.
First, we create descriptive statistical summaries of the participant response to address how geographic researchers define reproducibility, their familiarity and experience with reproducible research practice, and the barriers to reproducibility they perceive in the discipline.
Second, we conducted an analysis of the experience of the subset of geographic researchers who reported attempting independent reproductions of prior work during the last two years that identified what motivated reproduction attempts, how successful those attempts were, and what factors hindered success.
Given the topical and epistemological variation that exists among geographic researchers, we examined differences by disciplinary subfield and methodological approach as part of each analysis.

@@

\textit{Definition:} Before providing a common definition of reproducibility, we asked each participant to provide their own definition.
We measured the similarity of each provided definition to the definition of adopted by the \citet{NASEM2019}. 
The NASEM defines reproducible research as having four characteristics --- same data, same procedure, same results, and same context.
To make this comparison, two of the authors independently coded each provided definition for the presence/absence of each of the four characteristics included in the NASEM definition.
Disagreements in the assignment of codes were resolved through discussion between the two authors. 
As a final check, the third author reviewed rectified coding and resolved any remaining disputes.
To create an aggregate measure of agreement the final coded response for each participant was then summed across the four characteristics, creating definition similarity \textit{d} with domain [0, 4].

\textit{Familiarity and Experience:} We measured participant familiarity and experience with five reproduciblity enhancing research practices; the use of --- open source software, research notebooks, data sharing, code sharing, and pre-registration. 
We created a summary measure of research familiarity with these practices, \textit{f}, by summing the number of reproducible practices a researcher was 'somewhat' or 'very' familiar with.
To assess researcher experience with these same five practices, we created \textit{p}, which counts the number of practices a researcher reported using 'most of the time' or 'always' when conducting their own research. 
Both \textit{f} and \textit{p} have domains [0,5].

@@

Our second analysis examines only researchers that reported attempting a reproduction in the past two years. 
We asked each of these researchers what motivated their reproduction attempt. 
Two of the authors independently assigned these responses to groups with the following motivations - i) verification/check of published research, ii) an internal check of their own research to verify their work and increase the transparency of their work, ii) a desire to learn from past work, or use the reproduction in teaching. 
Some authors provided motivation linked to the replication of results in new geographic contexts. 
Because these responses did not match our provided definition of reproduction, we removed these from the subsample. 
We identified disagreements in motivation assignments, and the third author again resolved all disputes in consultation with the two assigning authors.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Survey Response Demographics}
A total of \textit{n}=218 of the authors we contacted completed the online survey with information sufficient for analysis. 
The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent. 
The refusal rate was 3.1 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
Respondents were similarly well balanced across the disciplinary subfields - human geography (30.7\%), physical geography (29.8\%), nature and society (10.1\%), geographic methods and GIScience (28.0\%); and methodological approaches - quantitative (42.2\%), qualitative (18.3\%), and mixed-methods (39.0\%) research.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Researcher Perspectives on Reproducibility}
A primary aim of our survey was to establish how geographic researchers conceptualize reproducibility and their current level of knowledge and experience with reproducibility enhancing research practices.
Nearly all researchers reported being at least somewhat familiar with the term reproducibility (89.0\%) with half reporting being very familiar with the term (53.6\%).
A majority of researchers also believe reproducibility is compatible with epistemologies used in the discipline (58.2\%). 
However, researchers estimated that only half of the results published in the discipline were reproducible, albeit with wide variance ($\overline{rep}=50.6\%$, $\sigma=24.7\%$), and reported limited familiarity with and use of many reproducible research practices. 
Few respondents reported attempting to reproduce the work of other researchers (14.7\%) with fewer still attempting to publish those reproduction studies (6.8\%).

Table \ref{tab:overview} summarizes how  researchers define reproducibility (\textit{d}), their familiarity with (\textit{f}) and use of (\textit{p}) reproducible research practices, and the factors they see as barriers (\textit{b}) to reproducibility in geography. 
We present the mean and standard deviation for the overall sample and for each subfield and methodological approach.
The following sub-sections discuss each of these topics in turn.

@@

%%%%%%%%%%%
\subsubsection*{Definitions and Importance of Reproducibility}
A total of \textit{$n_{d}$}=181 (83.0\%) of our survey respondents provided an interpretable definition of reproducibility.  
On average, geographic researchers provided definitions of reproducibility that generally explicitly included one to two ($\overline{d}=1.83$) of the four characteristics from the definition adopted by the NASEM.
This level of inclusion was consistent across subfields and methodological approaches.
The availability and use of the same research procedures (80.7\%) and results (74.0\%) were the characteristics of reproducibility most frequently identified by researchers. 
Less than half of respondents explicitly included use of the same data (38.1\%) or the need to work in the same context (17.7\%) in their definitions. 
This patterns was also consistent across subfields and approaches, with a slightly greater emphasis on data and procedural consistency and availability amongst quantitative and methods focused researchers.
The lower inclusion of data and context in definitions matched the conflation of reproduction and replication by a minority of researchers (20.4\%).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Introduction}
Reproducibility is important for geography for the same reason it is important in other fields - one-off studies 
Reproducibility as a characteristic of a study that lends it credibility v. Reproducibility as a error correcting function of science.

While geographers continue to debate the role of reproduction studies in the discipline \citep{kedron2022replication}, examine the reproducibility of individual studies \citep{Nust_AGILE_2022, kedron2021GA}, and build the infrastructure needed to support reproducible research \citep{wilson2021}, no one has conducted a systematic survey of the use of reproducible research practices in the discipline.

Within geography, reproduction efforts have identified the inaccessibility of data, code, and information about the computational environment as key barriers to recreating results. 
Irreproducibility has also been linked to conceptual and methodological transparency as researchers make decisions about the handling of spatial forms of uncertainty \citep{kedron2021GA}. 
While these efforts have produced useful reproducibility guidance for geographic researchers \citep{hofer2019reproducible, wilson2021} they have not been systematic surveys of the discipline as a whole.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Assessing the Reproducibility of Research}

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{The Evidence Currently Available from Reproducibility Assessments}
The reproducibility of research can be assessed directly by attempting to recreate the results of selected studies, or indirectly by reviewing the availability of the research components (e.g., data and code) or surveying those working in that field about their research practices. 
Direct assessments of reproducibility provide insight into how a particular study was conducted and why a consistent result could, or could not, be obtained.  
However, such assessments are resource and time intensive, which makes it difficult to gather information from numerous studies. 
Constrained to a limited number of studies, direct assessments offer only suggestive evidence about the reproducibility of unevaluated studies and the prevalence of reproducible research practices. 
In contrast, comparatively less resource intensive indirect assessments that catalog reproducible research practices across many studies offer less insight into individual studies, but provide evidence of how common reproducible research practices are and, by extension, how reproducible work in a field of study is likely to be.

Across many disciplines, direct reproduction attempts remain relatively rare \citep[see][]{chang2015economics, moraila2014measuring, iqbal2016reproducible,sumner2020reproducibility}.
However, prominent attempts to reproduce research in economics \citep{chang2015economics}, computer science \citep{moraila2014measuring}, and psychology \citep{open2015estimating} have all been able to reproduce only a small portion of studies because original authors did not share data or adequate information about their procedures.

Within geography, the small number of available reproduction attempts similarly suggest that many studies cannot be fully reproduced, or are simply missing the components needed to attempt a reproduction \citep{nust2018, Kedron2021ssrn, konkol2019, ostermann2021, Nust_AGILE_2022}.
For example, \citet{ostermann2021}'s attempt to reproduce the computational analyses of 75 papers published in the GIScience conference series found that most results could not be reproduced, or could only be reproduced with significant effort. 
\citet{konkol2019}'s attempt to reproduce 41 geocomputational studies likewise found that 39 of the papers had coding issues that hindered reproduction and that 47 percent of the figures created using the original data and code deviated from the those published in some significant way (e.g., graphs with different curves). 
A series of reproduction attempts by \citet{Kedron_MollaloRP, Kedron_SaffaryRP, Kedron_VijayanRP} and \citet{paez2022reproducibility} show that the issues hindering the reproduction of results extend beyond computation and into the conceptualization and design of geographic research.
Nonetheless, like reproduction attempts in other disciplines these studies provide only suggestive evidence of underlying problems, not a comprehensive assessment of the prevalence or sources of these issues.

Indirect reproducibility assessments offer a wider view of what and how common these underlying issues may be. 
The available evidence for study reviews suggests inadequate record keeping, opaque reporting, unavailable research components, and a lack of incentives are likely important factors contributing to the irreproducibility of research \citep{NASEM2019}. 
Systematic reviews of publications in prominent outlets \citep{byrne_2017,stodden2018empirical} suggest these issues are likely widespread. 
Reproducibility surveys paint a similar picture. 
Recent surveys suggest that the majority of scientists have either not tried, or tried and failed to reproduce another scientist's work \citep{baker20161, boulbes2018survey}. 
Moreover, a sizable portion of the researchers responding to these surveys admit to engaging in questionable research practices linked to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.
These findings match researcher perceptions, which link irreproducibility to causes ranging from natural variation to outright fraud \citep{ranstam2000fraud, anderson2007normative, baker20161}.

To date only a handful studies have attempted to indirectly measure the reproducibility of geographic research.
In a survey of remote sensing editors and working group officers of the International Society for Photogrammetry and Remote Sensing, \citet{balz2020reproducibility} asked respondents whether they believe a reproducibility crises existed in their sub-field, but not what the causes of such a crisis might be.
In a richer treatment of the issue, \citet{konkol2019} survied of participants from the 2016 European Geosciences Union General Assembly to assess the frequency with which researchers published their work in ways that enabled computational reproducibility. 
Those authors found that only 33 percent of respondents included links to the data used in their analyses and only 12 percent provided their analytical code. 
The authors also found that only seven percent of respondents ever attempted to reproduce the work of other researchers.
Similarly, in a literature review of volunteered geographic information research, \citet{ostermann2017} found the computational reproducibility of work in the sub-field limited by the availability of original data, metadata, source code, or pseudocode.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Limitations of the Currently Available Evidence}
While it may not be possible to determine the extent of irreproducibility across or within disciplines from available studies, it is possible to draw lessons about potential sources of irreproducibility.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Current State of Knowledge}

Most indirect assessments sample studies for review from conveniently accessible archives, such as conference paper series \citep{gundersen2018state, ostermann2017}, or target specific journals and disciplinary repositories \citep{stodden2018empirical, stodden2018enabling, byrne_2017}.
These assessments have also tended to focus on evaluating the computational components of research such as data and code availability, as this information is easier to identify and assess at scale when compared to components like field procedures or qualitative analysis that may be included only in text. 
Surveys of researcher practices and attitudes on reproducibility face similar challenges. 
Rather than carefully defining researcher populations of interest, existing surveys have drawn data non-randomly from self-selecting populations that are convenient to survey (e.g., members of professional association, conference attendees), but are not necessarily representative of researchers active in a particular field. 
These surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response.

Across many disciplines, direct reproduction attempts remain relatively rare, and those that do exist \citep[see][]{chang2015economics, moraila2014measuring, iqbal2016reproducible,sumner2020reproducibility} have selectively targeted publications in high-impact journals and conference papers series in a limited number of disciplines that are not representative of many forms of research.

Despite their growing number, the available body of both direct and indirect reproducibility assessments currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically \citep{NASEM2019}.
This knowledge gap exists because neither direct nor indirect reproducibility assessments have been designed so the results of the sample of studies evaluated can be extended to the population of research as a whole.

Overall, we have yet to assess the use of reproducible research practices across the discipline's diverse research traditions, or identify the factors that have barred geographers from adopting practices that foster reproducibility or from conducting more reproduction studies.
Our knowledge and systems remain incomplete because

the evidence available from direct and indirect assessments of reproducibility suggests that studies are often not reproducible because researchers do provide the information or materials others need to recreate their work.

Which leaves a set of basic questions about the reproducibility of geographic research unanswered.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data and Methods}
Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Reproducibility in Geographic Research Repository (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF).
That repository connects to a Github repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
All of the results presented in this paper can be independently reproduced using the materials in that repository.
Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_Survey_PAP} - \url{https://osf.io/6zjcp}). 
The survey was conducted under the approval and supervision of the Arizona State Institutional Review Board - \textit{STUDY00014232}.

@@

Second, we used Arizona State University's institutional subscription to the \href{https://www.scopus.com/home.uri}{Scopus Database} to extract journal information (e.g., subject area, ranking), article information (e.g., abstract, citation counts), and author information (e.g., corresponding status, email) for each publication. 
Because our intention was to capture individuals actively publishing new geographic research, we retained publications indexed by Scopus as \textit{document type = "Article"} and removed all other publication types (e.g., editorials, book reviews) from our article database. 
We also removed articles with missing authorship information.

Third, we created a list of researchers and their published articles, focusing on corresponding authors for two reasons.
(1) Corresponding authorship is one indicator of the level of involvement an individual had in a given work. 
While imperfect, it was the best available indicator in the Scopus database as across journals there is no commonly adopted policy for declarations of author work (e.g., CRediT Statements).
(2) Scopus maintains email contact information for all corresponding authors, which gave us a means of contacting researchers in our sampling frame.
Scopus also maintains a unique identifier for each author (author-id) across time, which allowed us to identify authors across publications.

Fourth, we constructed a sampling frame of unique researchers and their most recent email contact information. 
We determined uniqueness by grouping researchers by their author-id, and we selected for the most recent contact information by selecting records associated with the most recent year of publication. 
For 383 researchers who had two or more distinct emails in the latest year of publication, we removed non-institutional personal email addresses and then selected one of the remaining institutional email address.

Applying these criteria yielded a sampling frame of 29,828 researchers. 
On average, these authors published 2.7 articles in geography journals meeting our criteria between 2017 and 2021. 
Roughly one-third (33.0\%) were most recently a corresponding author for an article published in a general geography journal. 
A similar proportion (32.0\%) were most recently a corresponding author for an article published in an earth sciences journal, and smaller proportions in the social sciences and cultural geography (20.0\% and 16.0\%, respectively).

\subsection*{Survey Instrument}
The survey consisted of 23 questions that assess (i) perceptions of the reproducibility of geographic research, (ii) familiarity and use of reproducible research practices, and (iii) beliefs about barriers to reproducibility, and (iv) experience conducting independent reproductions. 
Survey questions were developed following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility literature. 
All researchers were presented questions about their definition of reproducibility, familiarity with and use of reproducible practices, and perceptions of barriers to reproducibility. 
A subset of researchers that reported attempting to reproduce a study in the past two years were given an additional set of questions about their experience conducting that work.

We pilot tested the survey instrument with a subset of \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
After pilot testing we removed these individuals from our sampling frame to ensure they would not be included in our final sample.

@@

%%%%%%%%%%%
\subsubsection*{Statistical Approach}
We conduct two statistical analyses of the survey response.
First, we create descriptive statistical summaries of the participant response to address how geographic researchers define reproducibility, their familiarity and experience with reproducible research practices, and the barriers to reproducibility they perceive in the discipline.
Second, we conducted an analysis of the experience of the subset of geographic researchers who reported attempting independent reproductions of prior work during the last two years.
That analysis identified what motivated reproduction attempts, how successful those attempts were, and what factors hindered success.
Given the topical and epistemological variation that exists among geographic researchers, we examined differences by disciplinary subfield and methodological approach as part of each analysis.

@@

\textit{Definition:} Before providing a common definition of reproducibility, we asked each participant to provide their own definition of the term.
We coded these definitions following two procedures.
First, we measured the similarity of each provided definition to the definition of adopted by the \citet{NASEM2019}. 
The NASEM defines reproducible research as having four characteristics --- same data, same procedure, same results, and same conditions.
To make this comparison, each of the authors independently coded each respondent definition for the presence/absence of each of the four characteristics included in the NASEM definition.
Disagreements in the assignment of codes were resolved through discussion between the three authors.
To create an aggregate measure of agreement the final coded response for each participant was then summed across the four characteristics, creating definition similarity \textit{d} with domain [0, 4].

Second, we coded each definition to one of three motivations for ensuring the reproducibility of a study--- to facilitate the assessment of prior work, to improve transparency and facilitate further extension of work, and to improve the transparency and consistency of study data.
We derived this coding from common themes in the authors response and our own reading of the reproducibility literature.
As above, each definition was independently coded by each author before code assignments across authors were compared with disagreements resolved through discussion.

\textit{Familiarity and Experience:} We measured participant familiarity and use of five reproduciblity enhancing research practices; the adoption of--- open-source software, research notebooks, data sharing, code sharing, and research plan preregistration. 
We created a summary measure of familiarity with these practices, \textit{f}, by summing the number of reproducible practices a researcher was 'somewhat' or 'very' familiar with.
To assess experience with these same five practices, we created \textit{p}, which counts the number of practices a researcher reported using 'most of the time' or 'always' when conducting their own research. 
Both \textit{f} and \textit{p} have domains [0,5].

@@

Our second analysis examined only researchers that reported attempting a reproduction in the past two years. 
We asked each of these researchers what motivated their reproduction attempt. 
Two of the authors independently assigned these responses to groups with the following motivations - i) verification/check of published research, ii) an internal check of their own research to verify their work and increase the transparency of their work, iii) replication of a study with new data, and iv) a desire to learn from past work, or use the reproduction in teaching. 
We identified disagreements in motivation assignments, and the third author again resolved all disputes in consultation with the two assigning authors.
We selected groups i) and iv) for further analysis of reproduction attempts, as these motivations most closely matched our definition of reproduction.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Survey Response Demographics}
A total of \textit{n}=218 of the authors we contacted completed the online survey with information sufficient for analysis. 
The contact rate for the survey was 13.9 percent and the cooperation rate was 77.6 percent, yielding an overall response rate of 10.8 percent. 
The refusal rate was 3.1 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
Respondents were similarly well balanced across the disciplinary subfields - human geography (30.7\%), physical geography (29.8\%), nature and society (10.1\%), geographic methods and GIScience (28.0\%); and methodological approaches - quantitative (42.2\%), qualitative (18.3\%), and mixed-methods (39.0\%) research.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Researcher Perspectives on Reproducibility}
A primary aim of our survey was to establish how geographic researchers conceptualize reproducibility and their current level of knowledge and experience with reproducibility enhancing research practices.
Nearly all researchers reported being at least somewhat familiar with the term reproducibility (89.0\%) with half reporting being very familiar with the term (53.6\%).
A majority of researchers also believe reproducibility is compatible with epistemologies used in the discipline (58.2\%). 
However, researchers estimated that only 50.6 percent of the results published in the discipline were reproducible, albeit with a large standard deviation of 24.7 percent that suggests great uncertainty about the true value. 
Few respondents reported attempting to reproduce the work of other researchers (14.7\%) with fewer still attempting to publish those reproduction studies (6.8\%).

Table \ref{tab:overview} summarizes how researchers define reproducibility (\textit{d}), their familiarity with (\textit{f}) and use of reproducible research practices (\textit{u}), and the factors they see as barriers (\textit{b}) to reproducibility in geography. 
We present the mean and standard deviation for the overall sample and for each subfield and methodological approach.
In aggregate, the data reveal trends in definition, familiarity, practices, and barriers of reproducibility between the sub-disciplines and methodological approaches. 
Respondents that self-identified as specializing in physical geography and geographic methods consistently report higher indicators than those working nature and society and human geography.
Similarly, respondents that identified as primarily using quantitative and mixed methods approaches consistently report higher indicators than those using qualitative methods.
The following sub-sections present detailed results for each of these topics, highlighting the principal sources of difference between sub-disciplines and methodological approaches.

@@

%%%%%%%%%%%
\subsubsection*{Definitions and Importance of Reproducibility}
A total of \textit{$n_{d}$}=181 (83.0\%) of our survey respondents provided an interpretable definition of reproducibility.  
On average, geographic researchers provided definitions of reproducibility that explicitly included one or two ($\overline{d}=1.83$) of the four characteristics from the definition adopted by the NASEM.
This level of inclusion was consistent across subfields and methodological approaches.
The availability and use of the same research procedures (80.7\%) and results (74.0\%) were the characteristics of reproducibility most frequently identified by researchers. 
Less than half of respondents explicitly included use of the same data (38.1\%) or the need to work in the same context (17.7\%) in their definitions. 
This pattern was consistent across subfields and approaches, with a slightly greater emphasis on data and procedural consistency and availability amongst quantitative and methods focused researchers.
The lower inclusion of data and context in definitions can be explained by researchers understanding reproducibility in terms of the formal NASEM definition of "replicability"--- a pattern evident in at least 20.4\% of respondents' definitions. For example, one respondent defines reproducibility as, "The extent to which the research design can be replicated in different geographical contexts."

Researchers' definitions of reproducibility were primarily connected to two epistemic functions.
Just over half of respondents (52.5\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies.
Nearly all other researchers (40.9\%) tied reproducibility to the need for transparency in research so others could independently expand upon past studies.
Identification of reproducibility with both of these functions was supported by responses to related questions from our entire sample (\textit{n}=218). 
A majority of researchers identified reproducibility as important for validating (75.2\%) and establishing the credibility (72.5\%) of research.  
Respondents also saw reproducing studies as important to reducing the presence of persistent errors in the discipline (77.5\%) and to increasing trust in research findings (78.45\%).
In parallel with the need for openness and transparency in science, most respondents agreed with the importance of reproducibility for research efficiency (63.3\%), communication with academics (68.8\%) and practitioners (64.7\%), and training students (75.7\%).

Despite wide recognition of reproducibility as epistemically important, respondents were cautious about drawing conclusions from a single study or reproduction attempt. 
Half of the respondents (50.9\%) agreed that when researchers don't share their data they have less trust in a study.
41.7 percent agreed that inability to reproduce a result detracts from the validity of a study, and a smaller minority agreed that such inability implies that the result is false (26.2\%).
